---
title: "Quick Start Guide"
output: rmarkdown::github_document
vignette: >
  %\VignetteIndexEntry{Quick Start Guide}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, echo = FALSE}
knitr::opts_chunk$set(collapse = FALSE,
                      comment = "##",
                      tidy = TRUE)
```

# Preliminaries

**conText** was designed to work closely with [quanteda](https://quanteda.io), as such most functions will expect a quanteda object such as a _corpus_, _tokens_ or _dfm_/_fcm_. To make the most of **conText**, we recommend that you familiarize yourself with some of quanteda's basic functionalities [Quick Start Guide](https://quanteda.io/articles/quickstart.html).

# Setup

## Installing the package

Since **conText** is not _yet_ available on CRAN you will need to install it directly from GitHub.

```{r, eval=FALSE}
devtools::install_github("prodriguezsosa/conText")
```

## Load package

```{r, message=FALSE}
library("conText")
```

# Data

To use **conText** you will need three datasets: 

1. A (quanteda) **corpus** with the documents and corresponding document variables (covariates) you want to evaluate.
2. A set of (GloVe) **pre-trained embeddings**.
3. A **transformation matrix** specific to the pre-trained embeddings.

The **conText** package includes two sample corpora `cr_sample_corpus` --a sample of the U.S. Congressional Records (Sessions 111th - 114th)-- and `anes2016_sample_corpus` --a sample of the ANES 2016 open-ended question on "most important isssues facing the country"--; a subset of [Stanford NLP's](https://nlp.stanford.edu/projects/glove/) 300-dimensional GloVe embeddings, `glove_subset`; and a transformation matrix ,`khodakA`, computed by [Khodak et al.](https://arxiv.org/abs/1805.05388) for the aforementioned GloVe 300-dimensional embeddings (see documentation for details). For the following guide we will be using the full versions of these datasets which we've made available [here](https://www.dropbox.com/sh/6dfr3i6no6nzvm0/AADqk6HFTvZJGNyu3FuO62kGa?dl=0).

## Load data

```{r, message = FALSE}

# other libraries
library(quanteda)
library(dplyr)

# path to data 
# set this path to wherever you stored the data files
path_to_data <- '~/Dropbox/GitHub/large_data/conText/data/' 

## load data

# full GloVe 300
glove_wvs <- readRDS(paste0(path_to_data, 'glove.rds'))

# transformation matrix fro GloVe 300
khodakA <- readRDS(paste0(path_to_data, 'khodakA.rds'))

# U.S. Congressional Record Sessions 111th - 114th (Obama years)
cr <- readRDS(paste0(path_to_data, 'congressional_record.rds'))
cr <- cr %>% distinct(speech, .keep_all = TRUE) # remove duplicate speeches

# sample corpus
set.seed(2021L)
cr_sample <- cr %>% sample_n(size = 10000)

## build corpora
cr_corpus <- corpus(cr_sample$speech, 
                    docvars = cr_sample[,c('party', 'gender')])
```

# The building blocks of `a la carte` embeddings

## 1. Build a corpus of contexts

Suppose we are interested in the semantics sorrounding the word _immigration_ in the U.S. Congress during the Obama years (sessions 111th - 114th). To explore this we will use our Congressional Record corpus, `cr_corpus`. We begin by identifying all instances of the **target** term --_immigration_-- in our corpus and, for each instance, store it's context-- the N words (N = 6 in this example) preceding and following the instance. We can do this in one step using the `conText::corpus_context` function. Notice, both the input, `x`, and the output are a quanteda `corpus-object`. Moreover, each document in `immig_corpus` --a context arround an instance of _immigration_-- inherits the document variables (`docvars`) of the document from whence it came and can be retrieved using `docvars`. 

```{r, message = FALSE}
# build a corpus of contexts sorrounding the target term "immigration"
immig_corpus <- corpus_context(x = cr_corpus, pattern = "immigration", window = 6L)
summary(immig_corpus, n = 3)
```

## 2. Build a document-feature-matrix

Given a corpus of contexts, we next build it's corresponding document-feature-matrix, namely a matrix where each row represents a given document's vector of feature counts. We do this using quanteda's `dfm` function.

```{r, message = FALSE}

# tokenize texts
immig_toks <- tokens(immig_corpus)

# create document-feature matrix
immig_dfm <- dfm(immig_toks)
immig_dfm[1:3,1:3]
```

## 3. Build a document-embedding-matrix

Given a `dfm`, a set of pre-trained embeddings, and a corresponding transformation matrix, we can proceed to embed each document (context) `a la carte`. We embed any given document by multiplying each of it's feature counts with its corresponding pre-trained feature-embedding, (column) summing the resulting vectors, and multiplying by the transformation matrix. We do so using `conText::dem`--`dem` standing for _document-embedding-matrix_. Keep in mind, if a given document has no features that overlap with the pre-trained embeddings provided, said document will be dropped. 

```{r, message = FALSE}

# create document-embedding matrix using a la carte
immig_dem <- dem(x = immig_dfm, pre_trained = glove_wvs, transform = TRUE, transform_matrix = khodakA, verbose = TRUE)

# you can see which documents where not embedded (in this example all documents are embedded)
# setdiff(docnames(immig_dfm), immig_dem@Dimnames$rows)

# to see the features that were used in creating the embeddings
head(immig_dem@features)
```

## 4. Average over document embeddings

We now have an ALC embedding for each context of `immigration` in our Congressional Record corpus. To get a single embedding for immigration, we can simply take the (column) average. However, we are often interested in exploring semantic differences as a function of covariates --e.g. party. To do so we simply average within a grouping variable defined by the covariates. We do this using `conText::dem_group` (very similar in flavor to quanteda's `dfm_group`). Notice, a `dem-class` object inherits all the document variables from the `dfm` used to compute it.

```{r, message = FALSE}

# to get a single "corpus-wide" embedding, take the column average
immig_wv <- colMeans(immig_dem)
length(immig_wv)

# to get group-specific embeddings, average within party
immig_wv_party <- dem_group(immig_dem, groups = immig_dem@docvars$party)
dim(immig_wv_party)

# the first 5 dimensions of each party's dense vector representation (embedding) of "immigration"
immig_wv_party[,1:5]
```

## 5. Comparing group embeddings

Given each party's embeddings, we can explore their differences using. We can evaluate differences in nearest neighbors --features with the highest cosine-similarity a given embedding-- using `conText::nns()` or explore their cosine similarity with specific features of interest using `conText::cos_sim()`. Notice, below we limit the set of candidate nearest neighbors to the set of features in our corpus.

```{r, message = FALSE}

# find nearest neighbors for overall immigraiton embedding
nns(immig_wv, pre_trained = glove_wvs, N = 5, candidates = immig_dem@features)

# find nearest neighbors by party
nns(immig_wv_party, pre_trained = glove_wvs, N = 5, candidates = immig_dem@features)

# compute the cosine similarity between each party's embedding and a specific set of features
cos_sim(immig_wv_party, pre_trained = glove_wvs, features = c('reform', 'enforcement'))
```

## Multiple Keywords

In the above example we had one keyword, `immigration`. However, we can also explore the semantics of multiple keywords simultaneously, including phrases! We simply provide a vector of patterns in the `pattern` argument.

```{r, message = FALSE}
# build a corpus of contexts sorrounding the target term "immigration"
mkws_corpus <- corpus_context(x = cr_corpus, pattern = c("immigration", "welfare", "immigration reform"), window = 6L)

# tokenize texts
mkws_toks <- tokens(mkws_corpus)

# create document-feature matrix
mkws_dfm <- dfm(mkws_toks)

# create document-embedding matrix using a la carte
mkws_dem <- dem(x = mkws_dfm, pre_trained = glove_wvs, transform = TRUE, transform_matrix = khodakA, verbose = TRUE)

# get keyword-specific embeddings
mkws_wvs <- dem_group(mkws_dem, groups = mkws_dem@docvars$pattern)

# find nearest neighbors for overall immigraiton embedding
nns(mkws_wvs, pre_trained = glove_wvs, N = 5, candidates = mkws_wvs@features)
```

# Wrapper functions

The above functions give users a lot of flexibility. However, it can be cumbersome to write each step separately every time we want to analyze a given target term. To facilitate this process `conText` includes three (for now) wrapper functions that allow you to do the above analysis and others with one line of code. An added advantage of the wrapper functions is that they make it easy to apply boostrapping --peform the analysis over random samples (with replacement) of the corpus and averaging. We being with `conText::get_nns`, a wrapper function to compare nearest neighbors between groups. Again, we limit the candidates to the set of features in our corpus.

```{r, message = FALSE}

# get local vocabulary (the intersect between features in the corpus and pre-trained embeddings)
local_vocab <- get_local_vocab(immig_corpus, pre_trained = glove_wvs)

# set seed to replicate sampling
set.seed(2021L)

# compare nearest neighbors between groups
get_nns(x = immig_corpus, N = 10,
        groups = docvars(immig_corpus, 'party'),
        candidates = local_vocab,
        pre_trained = glove_wvs,
        transform = TRUE,
        transform_matrix = khodakA,
        bootstrap = TRUE,
        num_bootstraps = 10)
```

Similarly, we can evaluate how similar each group's embedding is to a set of features of interest using `conText::get_cos_sim`. 

```{r, message = FALSE}

# set seed to replicate sampling
set.seed(2021L)

# compute the cosine similarity between each group's embedding and a specific set of features
get_cos_sim(x = immig_corpus,
            groups = docvars(immig_corpus, 'party'),
            features = c("reform", "enforce"),
            pre_trained = glove_wvs,
            transform = TRUE,
            transform_matrix = khodakA,
            verbose = FALSE)
```

The third wrapper function is `conText::contrast_nns`. This wrapper function is useful if we are comparing two groups and want to identify the terms that are significantly distinctive to each group. `contrast_nns` will compute an ALC embedding for each group, identify the union of the top N nearest neighbors and, for this set, compute the ratio cosine similarities. This ratio is informative of how much a given nearest neighbor is characteristic of one group. A ratio of $1$ for a given nearest neighbor indicates no difference between the two groups, while significant deviations from $1$ indicate the nearest neighbor is more distinctive to one of the two groups. If `bootstrap = TRUE`, this process will be repeated `num_bootstraps` times, sampling with replacement, to obtain standard erros around the cosine similarities for each group along with the ratio of these. If `permute = TRUE` then permutation will be used to identify ratios that significantly deviate from $1$. 

```{r, message = FALSE}

# set seed to replicate sampling
set.seed(2021L)

# compute ratio
cnns_df <- contrast_nns(x = immig_corpus,
groups = docvars(immig_corpus, 'party'),
pre_trained = glove_wvs,
transform = TRUE, transform_matrix = khodakA,
bootstrap = TRUE, num_bootstraps = 20,
permute = TRUE, num_permutations = 100,
candidates = local_vocab, N = 20,
verbose = FALSE)

# output
head(cnns_df)

# note: the numerator in the ratio is determined by 
# whichever group label is first.
unique(docvars(immig_corpus, 'party'))
```

We plot the output of `contrast_nns` using `conText::plot_ratio()` -- TO BE ADDED.

# Embedding regression

The above framework allows us to explore semantic differences over a given grouping variable. However, we may want to control for other covariates and, perhap more importantly, speak to the uncertainty sorrounding observed differences. In [Rodriguez, Spirling and Stewart (2021)](https://github.com/prodriguezsosa/EmbeddingRegression) we show how `a la carte` embeddings can be used within a regression-framework that allows us to perform statistical inference using embeddings. To do so we use the function `conText::conText()`. The data must be a quanteda corpus with covariates stored as document variables (`docvars`). 

First we specify the formula consisting of the target word of interest, _immigration_ and the set of covariates --this follows a similar syntax as R's `lm()` and `glm()` functions. To use all covariates in the corpus' docvars simply specify `immigration ~ .`. Similarly, if you want to embed the full documents rather than a specific target word, specify `. ~ party + gender`. Finally, the target argument can also be a phrase, simply wrap it in quotations -- e.g. `"immigration reform" ~ party + gender`. Covariates must either be binary indicator variables or discrete variables that can be transformed into binary indicator variables e.g. a character or factor variable with three states will be automatically transformed by `conText()` into two seperate indicator variables with one "baseline" state that is excluded from the regression.

Keep in mind, `conText()` calls on `corpus_context()`, so you do not need to create a corpus of contexts before running it, simply provide it with the original corpus and `conText()` will find all instances of the target word along with their respective contexts.

```{r, message = FALSE}
model1 <- conText(formula = immigration ~ party + gender,
                  data = cr_corpus,
                  pre_trained = glove_wvs,
                  transform = TRUE, transform_matrix = khodakA,
                  bootstrap = TRUE, num_bootstraps = 10,
                  stratify = TRUE,
                  permute = TRUE, num_permutations = 100,
                  window = 6, case_insensitive = TRUE,
                  verbose = TRUE)
```

`conText()` outputs a `conText-class` object which is simply a `dgCMatrix class` matrix corresponding to the beta coefficients (embeddings) with additional attributes including: a table with the normed coefficients (excluding the intercept), their std. errors and p-values, `@normed_coefficients` (see [Rodriguez, Spirling and Stewart (2021)](https://github.com/prodriguezsosa/EmbeddingRegression) for details), and the set of features used when creating the embeddings `@features`. 

Notice, we can combine the coefficients to compute the ALC embeddings for the various combinations of the covariates. 

```{r, message = FALSE}

# D-dimensional beta coefficients
# the intercept in this case is the ALC embedding for female Democrats
model1[,1:5]

# beta coefficients can be combined to get each group's ALC embedding
DF_wv <- model1['(Intercept)',] # (D)emocrat - (F)emale 
DM_wv <- model1['(Intercept)',] + model1['gender_M',] # (D)emocrat - (M)ale 
RF_wv <- model1['(Intercept)',] + model1['party_R',]  # (R)epublican - (F)emale 
RM_wv <- model1['(Intercept)',] + model1['party_R',] + model1['gender_M',] # (R)epublican - (M)ale 

# nearest neighbors
nns(rbind(DF_wv,DM_wv), N = 10, pre_trained = glove_wvs, candidates = model1@features)
```

We can also access and plot --using `plot_conText()`-- the normed coefficients.

```{r, message = FALSE}
model1@normed_cofficients
```

**PLOT HERE**

# Local GloVe and transformation matrix

If (a) you have a large enough corpus to train a full GloVe embeddings model and (b) your corpus is distinctive in some way --e.g. a collection of articles from scientific journals--, then you may want to consider estimating your own set of embeddings and transformation matrix. The first step is to estimate GloVe embeddings on the full corpus which you will then use as your pre-trained embeddings. 

## Estimate GloVe embeddings

This example is taken (with minor changes) from [this quanteda vignette](https://quanteda.io/articles/pkgdown/replication/text2vec.html) on computing GloVe embeddings using `quanteda` and `text2vec`.

```{r, message=FALSE, eval=FALSE}
library(text2vec)

#---------------------------------
# estimate transform
#---------------------------------

# tokenize
cr_toks <- tokens(cr_corpus)

# only use features that appear at least 5 times in the corpus
feats <- dfm(cr_toks, verbose = TRUE) %>%
    dfm_trim(min_termfreq = 5) %>%
    featnames()

# leave the pads so that non-adjacent words will not become adjacent
cr_toks <- tokens_select(cr_toks, feats, padding = TRUE)

# construct the feature co-occurrence matrix
cr_fcm <- fcm(cr_toks, context = "window", window = 6, count = "frequency", tri = FALSE)

# estimate glove model using text2vec
glove <- GlobalVectors$new(rank = 300, 
                           x_max = 10,
                           learning_rate = 0.05)
wv_main <- glove$fit_transform(cr_fcm, n_iter = 10,
                               convergence_tol = 1e-3, 
                               n_threads = RcppParallel::defaultNumThreads())


wv_context <- glove$components
cr_glove_wvs <- wv_main + t(wv_context) # word vectors

# qualitative check
local_vocab <- get_local_vocab(cr_corpus, pre_trained = cr_glove_wvs)
find_nns(cr_glove_wvs['immigration',], pre_trained = cr_glove_wvs, N = 5, candidates = local_vocab)
```

## Estimating the transformation matrix

Given a corpus and it's corresponding GloVe embeddings, we can compute a corresponding transformation matrix using `conText::compute_transform()`.

```{r, message = FALSE, eval=FALSE}
# compute transform
cr_transform <- compute_transform(x = cr_fcm, pre_trained = cr_glove_wvs, weighting = 100)
```


```{r, message = FALSE, eval=FALSE}
#---------------------------------
# check
#---------------------------------

# create document-embedding matrix using our locally trained GloVe embeddings and transformation matrix
immig_dem_local <- dem(x = immig_dfm, pre_trained = cr_glove_wvs, transform = TRUE, transform_matrix = cr_transform, verbose = TRUE)

# take the column average to get a single "corpus-wide" embedding
immig_wv_local <- colMeans(immig_dem_local)

# find nearest neighbors for overall immigraiton embedding
find_nns(immig_wv_local, pre_trained = cr_glove_wvs, N = 10, candidates = immig_dem_local@features)

# we can also compare to corresponding pre-trained embedding
sim2(x = matrix(immig_wv_local, nrow = 1), y = matrix(cr_glove_wvs['immigration',], nrow = 1), method = 'cosine', norm = 'l2')
```

# Other

## Feature embedding matrix

We can use a featur-co-occurrence matrix to simultaneously embed multiple features.

```{r, message = FALSE, eval=FALSE}

# terms of interest
features <- c('immigration', 'welfare')

# tokenize texts
cr_toks <- tokens(cr_corpus)

# create feature co-occurrence matrix
cr_fcm <- fcm(cr_toks, context = "window", window = 6, count = "frequency", tri = FALSE) %>% # set tri = FALSE to work with fem
  .[features,] # subset rows to features of interest

# compute feature-embedding matrix
cr_fem <- fem(cr_fcm, pre_trained = glove_wvs, transform = TRUE, transform_matrix = khodakA, verbose = FALSE)

# find nearest neighbors
nns(x = cr_fem, pre_trained = glove_wvs, N = 10, candidates = NULL)
```

## Embedding full documents

In this example we use open-ended responses to ANES 2016 question: "what are the most important issues facing the country?". Instead of embedding contexts around a given set of target words we embed each full open-ended response and average over respondent ideology.

```{r, message = FALSE}

# ANES 2016 open-ends on most important issues facing country
anes2016 <- readRDS(paste0(path_to_data, 'anes2016.rds')) %>% select(response, ideology, gender) %>% na.omit()

## build corpus
anes2016_corpus <- corpus(anes2016$response, 
                          docvars = anes2016[,c('ideology', 'gender')])

# tokenize texts
anes2016_toks <- tokens(anes2016_corpus)

# create document-feature matrix
anes2016_dfm <- dfm(anes2016_toks)

# create document-embedding matrix using a la carte
anes2016_dem <- dem(x = anes2016_dfm, pre_trained = glove_wvs, transform = TRUE, transform_matrix = khodakA, verbose = TRUE)

# group by ideology
anes2016_wv_ideology <- dem_group(x = anes2016_dem, groups = anes2016_dem@docvars$ideology)

# check nearest neighbors
nns(x = anes2016_wv_ideology, pre_trained = glove_wvs, N = 10, candidates = NULL)
```
